Hydra Battles in Coq

### 2020-11-02 doc/hydras.tex
Minor corrections

Definition mult_alpha_n  (alpha : t) (p : nat): t :=
  match alpha, p with
 |  (0,0), _  => zero
 |  _, 0 => zero
 |  (0, n), p => (0, n * p)
 |  ( n, b),  n' => ( n *  n', b)
               end.
Infix "*" := mult_alpha_n : o2_scope.

@@

Definition mult_n_alpha (n:nat)(alpha : t) : t :=
  match n, alpha with
 |  0, _  => zero
 |  _, (0,0) => zero
 |   n , (0,n') => (0, (n*n')%nat)
 |  n, (n',p') => (n', (n * p')%nat)
 end.

@@

Example e2 :  mult_n_alpha 3 (omega * 7 + 15) = omega * 7 + 45.
Proof. reflexivity. Qed.
\end{Coqsrc}

@@

   Remark Ltb_ij : Nat.ltb i j.
   Program Definition iota_ij  (alpha: t i) : t j :=  alpha.

@@

  End Inclusion_ij.

@@

Note that the elements of  \texttt{ON\_mult (FinOrd 3) Omega} are differently ordered (without limit ordinals):
\[(0,0),(1,0),(2,0),(0,1),(1,1),(2,1),(0,2),(1,2),(2,2),(0,3),\dots\]
(no limit ordinals).

@@

% \begin{itemize}
% \item First, we chose to write a version for sort \texttt{Type}, since versions
% for sorts \texttt{Prop} and \texttt{Set} can be easily derived from
% the former one. According to \emph{Coq}'s naming politics, we will call our 
% principle \texttt{oplus\_rect}

@@

In the present chapter, we  compare our implementation of the segment $[0,\epsilon_0)$ with a mathematical text in order to ``validate'' our constructions.
We chose as reference the axiomatic definition of the set of countable ordinals,
in chapter V of Kurt Schütte's book `` Proof Theory ''~\cite{schutte}.

@@

\begin{Coqsrc}
Fixpoint mult_Sn (alpha:Ord)(n:nat){struct n} :Ord :=
 match n with 
            | 0 => alpha
            | S p => mult_Sn alpha p + alpha
 end.

Definition mult_n alpha n :=
  match n with
      0 => zero
    | S p => mult_Sn alpha p
  end.

Notation "alpha * n" := (mult_n alpha n) : schutte_scope.
\end{Coqsrc}

@@

Theorem inject_mult_n (alpha : T1)  :
  nf alpha -> forall n:nat , inject (alpha *  n)%t1 =  inject alpha * n.

@@

\subsubsection*{Proof of $\psi(\omega,8]\times 13+56 < \psi(\omega,8]\times 13+57 $}

@@

\vspace{4pt}
\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Infix notations}
\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality \tnote{1} & \pageref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
\texttt{plus} & \texttt{alpha + beta} & $\alpha + \beta$ & ordinal addition & \pageref{sect:infix-plus-T1} ,\dots\\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \pageref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & one round of a battle & \pageref{sect:infix-round} \\
\texttt{rounds} & \texttt{h -+-> h'} & & one or more  rounds of a battle & \pageref{sect:infix-rounds} \\
\texttt{round\_star} & \texttt{h -*-> h'} & & any number of rounds of a battle & \pageref{sect:infix-rounds} \\

>>>>

Definition mult_fin_r  (alpha : t) (p : nat): t :=
  match alpha, p with
 |  (0,0), _  => zero
 |  _, 0 => zero
 |  (0, n), p => (0, n * p)
 |  ( n, b),  n' => ( n *  n', b)
               end.
Infix "*" := mult_fin_r : o2_scope.

@@

Definition mult_fin_l (n:nat)(alpha : t) : t :=
  match n, alpha with
 |  0, _  => zero
 |  _, (0,0) => zero
 |   n , (0,n') => (0, (n*n')%nat)
 |  n, (n',p') => (n', (n * p')%nat)
 end.

@@

Example e2 :  mult_fin_l 3 (omega * 7 + 15) = omega * 7 + 45.
Proof. reflexivity. Qed.
\end{Coqsrc}

@@

  Remark Ltb_ij : Nat.ltb i j.

  Program Definition iota_ij  (alpha: t i) : t j :=  alpha.

@@

  End Inclusion_ij.
\end{Coqsrc}

@@

Note that the elements of  (\texttt{ON\_mult (FinOrd 3) Omega}) are differently ordered (without limit ordinals):
\[(0,0),(1,0),(2,0),(0,1),(1,1),(2,1),(0,2),(1,2),(2,2),(0,3),\dots\]

@@

% \begin{itemize}
% \item First, we choose to write a version for sort \texttt{Type}, since versions
% for sorts \texttt{Prop} and \texttt{Set} can be easily derived from
% the former one. According to \emph{Coq}'s naming politics, we will call our 
% principle \texttt{oplus\_rect}

@@

In the present chapter, we  compare our implementation of the segment $[0,\epsilon_0)$ with a mathematical text in order to ``validate'' our constructions.
Our reference here is the axiomatic definition of the set of countable ordinals,
in chapter V of Kurt Schütte's book `` Proof Theory ''~\cite{schutte}.

@@

\begin{Coqsrc}
Fixpoint mult_Sn (alpha:Ord)(n:nat){struct n}: Ord :=
 match n with 
            | 0 => alpha
            | S p => mult_Sn  alpha p + alpha
 end.

Definition mult_fin_r alpha n :=
  match n with
      0 => zero
    | S p => mult_Sn alpha p
  end.

Notation "alpha * n" := (mult_fin_r alpha n) : schutte_scope.
\end{Coqsrc}

@@

Theorem inject_mult_fin_r (alpha : T1)  :
  nf alpha -> forall n:nat , inject (alpha *  n)%t1 =  inject alpha * n.

@@

\subsubsection*{Proof of $\psi(\omega,8)\times 13+56 < \psi(\omega,8)\times 13+57 $}

@@

\vspace{4pt}
\begin{table}[h]
  \centering
  \begin{threeparttable}
    \caption{Infix notations}
\begin{tabular}{|c|c|c|c|l|}
\hline
Name & Gallina&Math& Description& Page \\\hline
 \texttt{on\_lt} & \texttt{alpha o< beta}&$\alpha<\beta$& ordinal inequality \tnote{1} & \pageref{sect:on-lt-notation}\\
 \texttt{on\_le} & \texttt{alpha o<= beta}&$\alpha\leq\beta$& ordinal inequality & \pageref{sect:on-lt-notation}\\
\texttt{plus} & \texttt{alpha + beta} & $\alpha + \beta$ & ordinal addition & \pageref{sect:infix-plus-T1}, \dots\\
\texttt{oplus} & \texttt{alpha o+ beta} & $\alpha \oplus \beta$ & Hessenberg sum & \pageref{sect:infix-oplus} \\
\texttt{round} & \texttt{h -1-> h'} & & one round of a battle & \pageref{sect:infix-round} \\
\texttt{rounds} & \texttt{h -+-> h'} & & one or more  rounds of a battle & \pageref{sect:infix-rounds} \\
\texttt{round\_star} & \texttt{h -*-> h'} & & any number of rounds of a battle & \pageref{sect:infix-rounds} \\
